Manuscript progress report

### 2024-08-26 Docs/manuscript.Rmd
run small simulation for fGFPCA

```{r load_sim1}
load(here("Data/TrialRun/SimOutput_fGFPCA.RData"))
load(here("Data/TrialRun/SimOutput_GLMMadaptive.RData"))
load(here("Data/TrialRun/SimOutput_GFOSR_L1.RData"))
load(here("Data/TrialRun/SimOutput_GFOSR_L5.RData"))

@@

pred_list_GLMMad <- pred_list_GLMMad[1:5]
pred_list_GLMMad <- lapply(pred_list_GLMMad, function(x){
  colnames(x) <- name_vec
  return(x)
})

pred_list_gfofr <- lapply(pred_list_gfofr, function(x){
  x <- x %>% select(-window)
  colnames(x) <- name_vec
  return(x)
})

@@

```{r large_sim_plot, fig.height=8, fig.width=8}
bind_rows(
  pred_list_fGFPCA[[1]] %>% filter(id %in% rand_id) %>% 
    mutate(method="fGFPCA"),
  pred_list_GLMMad[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GLMMadaptive"),
  pred_list_gfofr[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GFOSR (L=1)"),
  pred_list_gfofr_l5[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GFOSR (L=5)") 
) %>% 
  mutate_at(vars(eta_i, starts_with("pred")), 
                .funs = function(x){exp(x)/(1+exp(x))}) %>%
  mutate(method=factor(method, 
         levels = c("fGFPCA", "GFOSR (L=5)", "GFOSR (L=1)","GLMMadaptive"))) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), na.rm = T)+
  geom_ribbon(aes(x=t, ymin=pred0.2_lb, ymax = pred0.2_ub,
                  col = "0.2", fill = "0.2", alpha = 0.1),
              linetype="dashed")+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), na.rm = T)+
  geom_ribbon(aes(x=t, ymin=pred0.4_lb, ymax = pred0.4_ub,
                  col = "0.4", fill = "0.4", alpha = 0.1),
              linetype="dashed")+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), na.rm = T)+
  geom_ribbon(aes(x=t, ymin=pred0.6_lb, ymax = pred0.6_ub,
                  col = "0.6", fill = "0.6", alpha = 0.1),
              linetype="dashed")+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), na.rm = T)+
  geom_ribbon(aes(x=t, ymin=pred0.8_lb, ymax = pred0.8_ub,
                  col = "0.8", fill = "0.8", alpha = 0.1),
              linetype="dashed")+
  guides(alpha = "none", col="none")+
  facet_grid(rows = vars(id), cols = vars(method))+
  labs(col = "Maximum observation time", x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(legend.position = "bottom")+
  scale_color_manual(values = cols)
```

@@

```{r}
data.frame(Method = c("fGFPCA", "GFOSR (L=5)", "GFOSR (L=1)","GLMMadaptive"), 
           Time = c(mean(time_fGFPCA),
                    mean(time_gfofr_l5),
                    mean(time_gfofr),
                    mean(time_GLMMad))) %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F)
```

@@

```{r}
cbind(calc_ISE(pred_list_fGFPCA, window),
      calc_ISE(pred_list_gfofr, window),
      calc_ISE(pred_list_gfofr_l5, window),
      calc_ISE(pred_list_GLMMad, window)) %>%
  data.frame(window = c("[0, 0.2]", "(0,2, 0.4]", "(0.4, 0.6]", 
                    "(0.6, 0.8]","(0.8, 1]"),
             ., 
             check.names = F) %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "fGFPCA" = 4, "GFOSR (L=5)" = 4, 
                     "GFOSR (L=1)" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" " = 1, "Maximum observation time" = 16)) %>%
  landscape()
```

@@

```{r}
cbind(calc_AUC(pred_list_fGFPCA, window),
      calc_AUC(pred_list_gfofr, window),
      calc_AUC(pred_list_gfofr_l5, window),
      calc_AUC(pred_list_GLMMad, window)) %>%
  data.frame(window = c("[0, 0.2]", "(0,2, 0.4]", "(0.4, 0.6]", 
                    "(0.6, 0.8]","(0.8, 1]"),
             ., 
             check.names = F) %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "fGFPCA" = 4, "GFOSR (L=5)" = 4, 
                     "GFOSR (L=1)" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" " = 1, "Maximum observation time" = 16)) %>%
  landscape()
```

@@

```{r, fig.height=4, fig.width=16}
bind_rows(calc_predint_cover(pred_list_fGFPCA) %>% mutate(method = "fGFPCA"),
          calc_predint_cover(pred_list_gfofr_l5) %>% mutate(method = "GFOSR (L=5)"),
          calc_predint_cover(pred_list_gfofr) %>% mutate(method = "GFOSR (L=1)"),
          calc_predint_cover(pred_list_GLMMad) %>% mutate(method = "GLMMadaptive")) %>%
  ggplot()+
  geom_line(aes(x=t, y=cover0.2, col = "0.2"), na.rm = T)+
  geom_line(aes(x=t, y=cover0.4, col = "0.4"), na.rm = T)+
  geom_line(aes(x=t, y=cover0.6, col = "0.6"), na.rm = T)+
  geom_line(aes(x=t, y=cover0.8, col = "0.8"), na.rm = T)+
  facet_grid(cols = vars(method))+
  labs(col = "Maximum observation time", x = "Time", y="Coverage rate")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(legend.position = "bottom")+
  scale_color_manual(values = cols)
```

>>>>

```{r load_sim1}
load(here("Data/SimN500/SimOutput_fGFPCA.RData"))
load(here("Data/SimN500/SimOutput_GLMMadaptive.RData"))
load(here("Data/SimN500/SimOutput_GFOSR_L1.RData"))
load(here("Data/SimN500/SimOutput_GFOSR_L5.RData"))

@@

# pred_list_GLMMad <- pred_list_GLMMad[1:5]
pred_list_GLMMad <- lapply(pred_list_GLMMad, function(x){
  colnames(x) <- name_vec
  return(x)
})

pred_list_gfofr_l1 <- lapply(pred_list_gfofr_l1, function(x){
  x <- x %>% select(-window)
  colnames(x) <- name_vec
  return(x)
})

@@

```{r large_sim_plot, fig.height=8, fig.width=8}
bind_rows(
  pred_list_fGFPCA[[1]] %>% filter(id %in% rand_id) %>% 
    mutate(method="fGFPCA"),
  pred_list_GLMMad[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GLMMadaptive"),
  pred_list_gfofr_l1[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GFOSR (L=1)"),
  pred_list_gfofr_l5[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GFOSR (L=5)") 
) %>% 
  mutate_at(vars(eta_i, starts_with("pred")), 
                .funs = function(x){exp(x)/(1+exp(x))}) %>%
  mutate(method=factor(method, 
         levels = c("fGFPCA", "GFOSR (L=5)", "GFOSR (L=1)","GLMMadaptive"))) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), na.rm = T)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), na.rm = T)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), na.rm = T)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), na.rm = T)+
  guides(alpha = "none", col="none")+
  facet_grid(rows = vars(id), cols = vars(method))+
  labs(col = "Maximum observation time", x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(legend.position = "bottom")+
  scale_color_manual(values = cols)
```

```{r large_sim_plot_ci, fig.height=8, fig.width=8}
bind_rows(
  pred_list_fGFPCA[[1]] %>% filter(id %in% rand_id) %>% 
    mutate(method="fGFPCA"),
  pred_list_GLMMad[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GLMMadaptive"),
  pred_list_gfofr_l1[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GFOSR (L=1)"),
  pred_list_gfofr_l5[[1]] %>% filter(id %in% rand_id) %>%
    mutate(method = "GFOSR (L=5)") 
) %>% 
  mutate_at(vars(eta_i, starts_with("pred")), 
                .funs = function(x){exp(x)/(1+exp(x))}) %>%
  mutate(method=factor(method, 
         levels = c("fGFPCA", "GFOSR (L=5)", "GFOSR (L=1)","GLMMadaptive"))) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"))+
  # geom_line(aes(x=t, y=pred0.2, col = "0.2"), na.rm = T)+
  geom_ribbon(aes(x=t, ymin=pred0.2_lb, ymax = pred0.2_ub,
                  col = "0.2", fill = "0.2", alpha = 0.1),
              linetype="dashed")+
  # geom_line(aes(x=t, y=pred0.4, col = "0.4"), na.rm = T)+
  geom_ribbon(aes(x=t, ymin=pred0.4_lb, ymax = pred0.4_ub,
                  col = "0.4", fill = "0.4", alpha = 0.1),
              linetype="dashed")+
  # geom_line(aes(x=t, y=pred0.6, col = "0.6"), na.rm = T)+
  geom_ribbon(aes(x=t, ymin=pred0.6_lb, ymax = pred0.6_ub,
                  col = "0.6", fill = "0.6", alpha = 0.1),
              linetype="dashed")+
  # geom_line(aes(x=t, y=pred0.8, col = "0.8"), na.rm = T)+
  geom_ribbon(aes(x=t, ymin=pred0.8_lb, ymax = pred0.8_ub,
                  col = "0.8", fill = "0.8", alpha = 0.1),
              linetype="dashed")+
  guides(alpha = "none", col="none")+
  facet_grid(rows = vars(id), cols = vars(method))+
  labs(col = "Maximum observation time", x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(legend.position = "bottom")+
  scale_color_manual(values = cols)+
  scale_fill_manual(values = cols)
```

@@

```{r}
data.frame(Method = c("fGFPCA", "GFOSR (L=5)", "GFOSR (L=1)","GLMMadaptive"), 
           Time = c(mean(time_fGFPCA),
                    mean(time_gfofr_l5),
                    mean(time_gfofr_l1),
                    mean(time_GLMMad))) %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F)
```

@@

```{r}
cbind(calc_ISE(pred_list_fGFPCA, window),
      calc_ISE(pred_list_gfofr_l1, window),
      calc_ISE(pred_list_gfofr_l5, window),
      calc_ISE(pred_list_GLMMad, window)) %>%
  data.frame(window = c("[0, 0.2]", "(0,2, 0.4]", "(0.4, 0.6]", 
                    "(0.6, 0.8]","(0.8, 1]"),
             ., 
             check.names = F) %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "fGFPCA" = 4, "GFOSR (L=5)" = 4, 
                     "GFOSR (L=1)" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" " = 1, "Maximum observation time" = 16)) %>%
  landscape()
```

@@

```{r}
cbind(calc_AUC(pred_list_fGFPCA, window),
      calc_AUC(pred_list_gfofr_l1, window),
      calc_AUC(pred_list_gfofr_l5, window),
      calc_AUC(pred_list_GLMMad, window)) %>%
  data.frame(window = c("[0, 0.2]", "(0,2, 0.4]", "(0.4, 0.6]", 
                    "(0.6, 0.8]","(0.8, 1]"),
             ., 
             check.names = F) %>%
  kable(digits = 3, booktabs=T,
        table.attr="style=\"color:black;\"") %>%
  kable_styling(full_width = F) %>% 
  add_header_above(c(" " = 1, "fGFPCA" = 4, "GFOSR (L=5)" = 4, 
                     "GFOSR (L=1)" = 4, "GLMMadaptive" = 4)) %>%
  add_header_above(c(" " = 1, "Maximum observation time" = 16)) %>%
  landscape()
```

@@

```{r, fig.height=4, fig.width=16}
bind_rows(calc_predint_cover(pred_list_fGFPCA) %>% mutate(method = "fGFPCA"),
          calc_predint_cover(pred_list_gfofr_l5) %>% mutate(method = "GFOSR (L=5)"),
          calc_predint_cover(pred_list_gfofr_l1) %>% mutate(method = "GFOSR (L=1)"),
          calc_predint_cover(pred_list_GLMMad) %>% mutate(method = "GLMMadaptive")) %>%
  ggplot()+
  geom_line(aes(x=t, y=cover0.2, col = "0.2"), na.rm = T)+
  geom_line(aes(x=t, y=cover0.4, col = "0.4"), na.rm = T)+
  geom_line(aes(x=t, y=cover0.6, col = "0.6"), na.rm = T)+
  geom_line(aes(x=t, y=cover0.8, col = "0.8"), na.rm = T)+
  facet_grid(cols = vars(method))+
  labs(col = "Maximum observation time", x = "Time", y="Coverage rate")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(legend.position = "bottom")+
  scale_color_manual(values = cols)
```
